Characterizing Stellar Streams by ML

### 2023-09-15 src/tex/ms.tex
[showyourwork] overleaf sync

            The astrometric track is modeled with a neural network, encompassing
            each phase space dimension, parameterized as a function of $\phi_1$.
            The neural network output for a single stream component is the mean
            location of the stream track in each dimension,
            $\astroM{\mbs{\mu}}(\phi_1)$, and its associated covariance matrix
            $\astroM{\mbs{\Sigma}}(\phi_1)$. The probability for the data is
            then
            \begin{equation}
                \cmp{S,w}{\pdf}(\nth{\mbs{w}} | \mbs{\theta}) \! = \mcal{N}_F {\transparent{0.5}\big(}\nth{\mbs{w}} | \astroM{\mbs{\mu}}\!(\phi_1), {\cmp{w}{\nth{\mbs{\Sigma}}}}^2 \! + \!  \astroM{\mbs{\Sigma}}^2\!\left(\phi_1\right) \!\big),
            \end{equation}
            where $\astroM{\mbs{\theta}}$ is the set of neural network
            parameters that define $\astroM{\mbs{\mu}}$ and
            $\astroM{\mbs{\Sigma}}$; and $\cmp{w}{\nth{\mbs{\Sigma}}}$ the data
            uncertainties.  In the simplest case, we take
            $\cmp{w}{\nth{\mbs{\Sigma}}}, \astroM{\mbs{\Sigma}}$ to be diagonal,
            consisting of both intrinsic dispersion for each dimension of
            $\mbs{w}$ and the data uncertainties added in quadrature. The data
            uncertainties $\cmp{w}{\nth{\mbs{\Sigma}}}$ are drawn from
            $\mbs{\delta}\mbf{W}$, the dataset of astrometric uncertainties (see
            \autoref{app:notation}).

@@

        % TODO: make this dynamically generated from the actual data.
        \begin{table}
            \centering
            \setlength{\tabcolsep}{0pt}
            \newcommand\capitem{\\$\phantom{+}\ast$\ }
            \caption{%
                Stream Track Regions Prior: %
                This table includes all the region priors used to guide the model towards the known stream track. The model will converge to the
                region $_{\rm minimum}^{\rm maximum}$.
                See \autoref{sub:methods:priors:track_region_prior} for details.
            }
            \label{tab:gd1_track_prior}
            {\rowcolors{2}{gray!10}{white!10}
            \begin{tabular}{@{}r<{\hspace{7pt}}*{4}{r<{\hspace{7pt}}}l<{\hspace{7pt}}@{}}
                \toprule
                component & $\phi_1 \,\unit{\degree}$ & $\phi_2 \,\unit{\degree}$ & $\mu_{\phi_1} \,[\frac{\rm{mas}}{\rm{yr}}]$ & $\mu \,\unit{mag}$ & $(\simeq \parallax \,\unit{mas})$ \\
                \midrule
                stream & -70 & & & ${\transparent{0.5}\big(}_{14.2}^{14.8}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.11}^{0.14}{\transparent{0.5}\big)}$ \\ 
                stream & -60 & ${\transparent{0.5}\big(}_{-2.55}^{\phantom{+}0.95}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-13.25}^{-11.75}{\transparent{0.5}\big)}$ & & \\ 
                stream & -50 & ${\transparent{0.5}\big(}_{-1.75}^{\phantom{+}1.75}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-14.05}^{-12.55}{\transparent{0.5}\big)}$ & & \\ 
                stream & -40 & ${\transparent{0.5}\big(}_{-1.75}^{\phantom{+}1.75}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-14.05}^{-12.55}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{14.1}^{ 14.7}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.11}^{0.15}{\transparent{0.5}\big)}$ \\
                spur & -35 & ${\transparent{0.5}\big(}_{\phantom{+}0.45}^{\phantom{+}2.15}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-15.95}^{\phantom{0}-9.95}{\transparent{0.5}\big)}$ & & \\
                stream & -30 & ${\transparent{0.5}\big(}_{-1.75}^{\phantom{+}1.75}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-13.35}^{-11.85}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{14.1}^{ 14.7}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.11}^{0.15}{\transparent{0.5}\big)}$ \\
                spur & -30 & ${\transparent{0.5}\big(}_{\phantom{+}0.45}^{\phantom{+}2.15}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-15.60}^{\phantom{0}-9.60}{\transparent{0.5}\big)}$ & & \\
                spur & -20 & ${\transparent{0.5}\big(}_{\phantom{+}0.65}^{\phantom{+}2.35}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-16.50}^{\phantom{0}-6.50}{\transparent{0.5}\big)}$ & & \\
                stream & 0 &  & & ${\transparent{0.5}\big(}_{14.7}^{15.3}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.09}^{0.15}{\transparent{0.5}\big)}$ \\
                \bottomrule\bottomrule
            \end{tabular}
            }
        \end{table}

>>>>

            The astrometric track is modeled with a neural network, encompassing
            each phase space dimension, parameterized as a function of $\phi_1$.
            The neural network output for a single stream component is the mean
            location of the stream track in each dimension,
            $\astroM{\mbs{\mu}}(\phi_1)$, and its associated covariance matrix
            $\astroM{\mbs{\Sigma}}(\phi_1)$. The probability for the data is
            then
            \begin{equation}
                \cmp{S,w}{\pdf}(\nth{\mbs{w}} | \mbs{\theta})
                \!= \mcal{N}_F \big(\nth{\mbs{w}} | \astroM{\mbs{\mu}}\!(\phi_1), {\cmp{w}{\nth{\mbs{\Sigma}}}}^2 \! + \!  \astroM{\mbs{\Sigma}}^2\!\left(\phi_1\right) \!\big),
            \end{equation}
            where $\astroM{\mbs{\theta}}$ is the set of neural network
            parameters that define $\astroM{\mbs{\mu}}$ and
            $\astroM{\mbs{\Sigma}}$; and $\cmp{w}{\nth{\mbs{\Sigma}}}$ the data
            uncertainties.  In the simplest case, we take
            $\cmp{w}{\nth{\mbs{\Sigma}}}, \astroM{\mbs{\Sigma}}$ to be diagonal,
            consisting of both intrinsic dispersion for each dimension of
            $\mbs{w}$ and the data uncertainties added in quadrature. The data
            uncertainties $\cmp{w}{\nth{\mbs{\Sigma}}}$ are drawn from
            $\mbs{\delta}\mbf{W}$, the dataset of astrometric uncertainties (see
            \autoref{app:notation}).

@@

        % TODO: make this dynamically generated from the actual data.
        \begin{table}
            \centering
            \setlength{\tabcolsep}{0pt}
            \newcommand\capitem{\\$\phantom{+}\ast$\ }
            \caption{%
                Stream Track Regions Prior: %
                This table includes all the region priors used to guide the model towards the known stream track. The model will converge to the
                region $_{\rm minimum}^{\rm maximum}$.
                See \autoref{sub:methods:priors:track_region_prior} for details.
            }
            \label{tab:gd1_track_prior}
            {\rowcolors{2}{gray!10}{white!10}
            \begin{tabular}{@{}r<{\hspace{7pt}}*{4}{r<{\hspace{7pt}}}l<{\hspace{7pt}}@{}}
                \toprule
                component & $\phi_1 \,\unit{\degree}$ & $\phi_2 \,\unit{\degree}$ & $\mu_{\phi_1} \,[\frac{\rm{mas}}{\rm{yr}}]$ & $\mu \,\unit{mag}$ & $(\simeq \parallax \,\unit{mas})$ \\
                \midrule
                stream & -70 & & & ${\color{gray}\big(}_{14.2}^{14.8}{\color{gray}\big)}$ & ${\color{gray}\big(}_{0.11}^{0.14}{\color{gray}\big)}$ \\ 
                stream & -60 & ${\color{gray}\big(}_{-2.55}^{\phantom{+}0.95}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-13.25}^{-11.75}{\color{gray}\big)}$ & & \\ 
                stream & -50 & ${\color{gray}\big(}_{-1.75}^{\phantom{+}1.75}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-14.05}^{-12.55}{\color{gray}\big)}$ & & \\ 
                stream & -40 & ${\color{gray}\big(}_{-1.75}^{\phantom{+}1.75}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-14.05}^{-12.55}{\color{gray}\big)}$ & ${\color{gray}\big(}_{14.1}^{ 14.7}{\color{gray}\big)}$ & ${\color{gray}\big(}_{0.11}^{0.15}{\color{gray}\big)}$ \\
                spur & -35 & ${\color{gray}\big(}_{\phantom{+}0.45}^{\phantom{+}2.15}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-15.95}^{\phantom{0}-9.95}{\color{gray}\big)}$ & & \\
                stream & -30 & ${\color{gray}\big(}_{-1.75}^{\phantom{+}1.75}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-13.35}^{-11.85}{\color{gray}\big)}$ & ${\color{gray}\big(}_{14.1}^{ 14.7}{\color{gray}\big)}$ & ${\color{gray}\big(}_{0.11}^{0.15}{\color{gray}\big)}$ \\
                spur & -30 & ${\color{gray}\big(}_{\phantom{+}0.45}^{\phantom{+}2.15}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-15.60}^{\phantom{0}-9.60}{\color{gray}\big)}$ & & \\
                spur & -20 & ${\color{gray}\big(}_{\phantom{+}0.65}^{\phantom{+}2.35}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-16.50}^{\phantom{0}-6.50}{\color{gray}\big)}$ & & \\
                stream & 0 &  & & ${\color{gray}\big(}_{14.7}^{15.3}{\color{gray}\big)}$ & ${\color{gray}\big(}_{0.09}^{0.15}{\color{gray}\big)}$ \\
                \bottomrule\bottomrule
            \end{tabular}
            }
        \end{table}
